---
title: "POLS/CS&SS 501: Assignment 1"
author: "Your Name"
output: html_document
---

<!-- knitr options -->
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Setup

Load any R packages, define any common packages.

These solutions use the **tidyverse** packages, and data for *QSS* included in the
**qss** R package.
<!-- message=FALSE suppresses the verbose messages printed when some packages are loaded -->
```{r message=FALSE}
library("tidyverse")
library("qss")
```

If it is not already installed, install **qss** using:
```{r eval=FALSE}
devtools::install_github("kosukeimai/qss")
```


# Exercise 1

Load the `turnout` dataset from the **qss** package.
```{r}
data("Kenya", package = "qss")
data("Sweden", package = "qss")
data("World", package = "qss")
```


Write answer here


# Exercise 2

Load the necessary datasets from the **qss** package.
```{r}
data("Kenya", package = "qss")
data("Sweden", package = "qss")
data("World", package = "qss")
```


Write answer here

# Exercise 3

Load the `leaders` dataset from the **qss** package.
```{r}
data("leaders", package = "qss")
```

Write answer here
